\documentclass{article}

\usepackage{lmodern}
\usepackage{amsmath,amsthm, amssymb}

\title{Good Problems}

\author{
    Ahmed Zaheer Dadarkar\\
    tymefighter
}

\begin{document}

    \maketitle

    \section{
        Number of Distinct Substrings that occur atleast twice in a
        given string
    }

    Essentially the solution is to add all those values of the lcp array
    which are greater than the next value, and also add the final value in
    the lcp array (i.e. the $n - 1$ indexed element). The lcp array is
    constructed using the suffix array by Kasai's Algorithm. \\
    The reason why this is true is that when $lcp[i] = x > 0$ for some i, then
    we already have $x$ strings that occur atleast twice. But we cannot simply
    add all the $lcp$ values since there may by substrings that are repeated.
    We can see that if $lcp[i - 1] > lcp[i]$, then $lcp[i - 1] - lcp[i]$
    substrings are unique, hence we can count them.

    \section{Maximum Number of Points that can be covered by a circle}

    You are given a set of points $S$ in the X-Y plane. You are alse given
    a the radius $r > 0$ of a circle which you must construct so as to maximize
    the number of points from $S$ which lie inside or on the circle.

    We initialize the answer by $1$ because we can construct the circle with
    any of the points as the center. Now, consider an optimal solution $C$
    which is a circle that covers the maximum number of points. If the number
    of points covered by $C$ is $1$, then we already have the answer since we
    initialize the answer by $1$. If the answer is greater than $1$, then
    consider the cases where the number of points that lie on the circle are
    less than $2$. The first case is when no point lies on the circle,
    then we translate the circle until atleast one point lies on it (we may
    end up in the second case by this). The second case is when a single point
    lies on the circle, now we pivot the circle at this point and rotate until
    atleast one more point is on the circle. Now that we have shown that an
    optimal solution exists which has alteast two points on the circle. \\
    We construct a solution by going over all possible pairs of points and
    constructing circle, and for each constructed circle we count how many
    points lie inside or on the circle. Then answer is the maximum over all
    these values.

    \section{All lengths to which a string can be compressed}

    \section{Number Of Occurrances of Every Prefix}

    \section{Small To Large}

    You are given a set $S = \{S_1, .., S_n\}$ consisting of $n$ multisets
    each currently containing a single element. You have to perform $n - 1$
    operations, in each operation you would be given $i$ and $j$ and you 
    have to merge the sets $S_i$ and $S_j$ and replace them with $S_{min(i,j)}$
    and then provide the number of distinct elements in that set.
    Method is that when asked to merge to sets, place the elements of the smaller
    set into the larger one.
    Now, consider any element $x \in \bigcup_{i = 1}^{n}S_i$, this element is
    added to a new set $O(\log n)$ times, the reason being that the size of the
    set this element is part of becomes atleast double of the previous one.
    Hence, after $m$ merges, we have

    \[
        2^m \leq n
    \]
    So, 
    \[
        m = O(\log n)
    \]
    Now, each add operation has $O(\log n)$ cost, hence for each element we
    have a total cost of $O(\log^2n)$, So for all elements together we
    have time complexity
    \[
        O(n \log^2n)
    \]

    \subsection{DSU using size of component}

    The method is that each time we are asked to merge two components, we
    make the node having subtree with larger size as the parent of the other
    Then at each such operation, we increase the size of the smaller tree
    by atleast a factor of 2.
    
    Hence, since each op costs $O(\log n)$, and there are $O(\log n)$
    such operations for \textbf{each} element, the total complexity is
    $O(n \log^2n)$

    \subsection{A Tree Problem}

    You are given a tree rooted at $0$ and a color on each node, you
    are then asked to compute the number of distinct colours in the
    subtree of each node. \\
    The method is to find out for each node which child is heavy,
    by heavy we mean that it has the largest size of subtree compared to
    other children. Then we merge the sets of all other children into
    the heavy child. \\
    An important thing to note is that we must not create a new set for the
    parent, instead we must keep the reference to the heavy child's set
    as the parent. \\
    For analysis, assume the color at each node is unique, meaning no other
    node has it. Now, pick color $c$ at any node(initially), then $c$ is moved
    at most $O(\log n)$ times since the set containing $c$ has it's size
    doubled at each operation. Also, cost of each operation is
    $O(\log {min(n, |C|)})$ where $C$ is the set of all colors, and when
    we consider all elements, we have the following complexity
    \[
        O(n (\log n) (\log{min(n, |C|)})) = O(n \log^2n)
    \]

    \section{Query for Number of Distinct elements in a Subarray}

    \section{References}

    \begin{itemize}
        \item https://cp-algorithms.com/string/z-function.html
        \item https://cp-algorithms.com/string/prefix-function.html
        \item http://codingwithrajarshi.blogspot.com/2018/06/small-to-large.html
        \item https://stackoverflow.com/questions/39787455/is-it-possible-to-query-number-of-distinct-integers-in-a-range-in-olg-n
    \end{itemize}
\end{document}